sta303-hw1

### 2025-02-07 sta303-hw1.Rmd
1
Rename Files

---
title: "sta303-hw1"
output: html_document
date: "2025-02-06"
---
t
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r cars}
library(MASS)  
library(ggplot2)
load("portugal.RData")

>>>>

---
title: "sta303-hw1"
output: html_document
date: "2025-02-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r cars}
library(MASS)  
library(ggplot2)
library(here)
load(here::here("data/Portugal.RData"))
